\documentclass{article}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[margin=1cm]{caption}
\usepackage{subcaption}
\usepackage{tcolorbox}
\usepackage{color}
\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}


\lstset{%
    % Basic design
    backgroundcolor=\color{editorGray},
    basicstyle={\small\ttfamily},   
    frame=l,
    % Line numbers
    xleftmargin={0.75cm},
    numbers=left,
    stepnumber=1,
    firstnumber=1,
    numberfirstline=false,
    }
\lstset{
    literate={~} {$\sim$}{1}
}

\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}

\oddsidemargin 0in \evensidemargin 0in
\topmargin -0.5in \headheight 0.25in \headsep 0.25in
\textwidth 6.5in \textheight 9in
\parskip 6pt \parindent 0in \footskip 20pt

% set the header up
\fancyhead{}
\fancyhead[L]{Stanford Aeronautics \& Astronautics}
\fancyhead[R]{Fall 2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\headrulewidth{0.4pt}
\setlength\headheight{15pt}
\input{preamble}

\usepackage{outlines}

\usepackage{xparse}
\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}
\usepackage{gensymb}

\newcommand{\ssmargin}[2]{{\color{blue}#1}{\marginpar{\color{blue}\raggedright\scriptsize [SS] #2 \par}}}


\setlength{\parindent}{0in}

\title{AA 274: Principles of Robotic Autonomy \\ Section 1: VM Installation, Git, Python}
\date{}

\begin{document}

\maketitle
\pagestyle{fancy}

Our goals for this section: \begin{enumerate}
	\item Install Ubuntu virtual machine locally.
	\item Learn how to use Git to pull assignments.
	\item Start working with Python and Numpy.
\end{enumerate}


\section{Installation}
For this class, we recommend using a virtual machine (VM) that we provide which has all the
required software preinstalled.
Alternatively, you can natively install Linux alongside your normal OS as a dual boot and install the required
packages yourself. This may give better performance, especially for graphics rendering. However, as there
can be driver issues and other edge cases that can come up when installing linux on hardware, we can only
officially support the VM in terms of providing help with your setup.
To set up the VM on your computer, follow the instructions here: 

\href{https://github.com/PrinciplesofRobotAutonomy/aa274-docker}{https://github.com/PrinciplesofRobotAutonomy/aa274-docker}

\section{Using Git}
Git is a source control tool that allows us to share code with you. To copy code for this section, type the following into your terminal:

 \begin{lstlisting}[escapechar=|]
 git clone https://github.com/StanfordASL/AA274_SECTION
\end{lstlisting}

You will use this folder to store all section material for the remainder of the class. So, to update this repo at the start of each section, type: 

 \begin{lstlisting}
 git pull
\end{lstlisting}

\section{Python}
Because our class is composed of students from AA, EE/ME, and CS, we will not assume that you have comprehensive coding knowledge. Therefore, the main purpose of this section is to get your coding skills spun up so you can work on the homework. If you know this material already, please help someone who doesn't know it as well.


In order to complete this part of our section, please switch to the scripts included in the code for this section.

\end{document}
